ZrO$_2$ Layer via Doctor Blading

### 2021-04-01 Process/article.tex
XRD added + process updated

\documentclass[a4paper]{article}
\usepackage[margin=2.5cm]{geometry}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{lipsum}
\usepackage{ngerman}
\usepackage{pdfpages}
\usepackage{hyperref}
\usepackage{url}
\usepackage{ragged2e} % to justify text
\newcommand{\todo}[1]{\textbf{\textcolor{red}{#1}}}
\newcommand{\td}[1]{\textbf{\textcolor{red}{#1}}}
\title{ZrO$_2$ Layer via Doctor Blading }
\author{Johann Dorn}

@@

\section{Doctor blading}
The temperature of the heating plate is set to 200 $^o$C.
The temperature of the vacuum plate is set and waited until reached.
The sample is placed on the vacuum plate and tested if it can be held by the under pressure.
The velocity is set and a mini test run is performed. 
The blade is put in position. 
100-125 $\mu$l of solution is applied with an 10-1000 $\mu$l pipette and the doctor blading is started immediately. 
After evaporation of the solution, the vacuum is turned of, the 'blade pusher' put into initial position, the blade removed and excess solution removed with a wipe. 
The small metal plate is transferred to the hot heating plate and rests on there for 3-5 min. 
The process is repeated as wished. 
\bibliographystyle{ieeetr}
\bibliography{fp}

>>>>

\documentclass[a4paper]{article}
\usepackage[margin=2.5cm]{geometry}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{lipsum}
\usepackage{ngerman}
\usepackage{pdfpages}
\usepackage{hyperref}
\usepackage{url}
\usepackage{ragged2e} % to justify text
\usepackage{amsmath}
\newcommand{\todo}[1]{\textbf{\textcolor{red}{#1}}}
\newcommand{\td}[1]{\textbf{\textcolor{red}{#1}}}
\title{ZrO$_2$ Layer via Doctor Blading }
\author{Johann Dorn}

@@

\section{Doctor blading}
The temperature of the heating plate is set to 200 $^o$C.
The temperature of the vacuum plate is set and waited until reached.
The sample is placed on the vacuum plate and tested if it can be held by the under pressure.
The velocity is set and a mini test run is performed. 
The blade is put in position. 
100-125 $\mu$l of solution is applied with an 10-1000 $\mu$l pipette and the doctor blading is started immediately. 
After evaporation of the solution, the vacuum is turned of, the 'blade pusher' put into initial position, the blade removed and excess solution removed with a wipe. 
The small metal plate is transferred to the hot heating plate and rests on there for 3-5 min. 
The process is repeated as wished.

\clearpage
\section{evaluation of one sample}
For every I-V curve (aluminium dot) the gradient $g$ at V=0 is calculated by taking 5 points after the origin and 5 points before the origin, averaging their V and I values and calculating i
\begin{equation}
	g = \frac{I_{n+1} - I_n}{V_{n+1} - V_n}.
\end{equation}
As a measure of conductance a distance D from an ideal non-conducting case. The average of the negative base 10 logarithm subtracted from an ideal non-conducting gradient of $10^{-13}$ 
\begin{equation}
	D = \sum_i^N \frac{ -log_{10}(g_i) - 13}{N}
\end{equation}
Another measure is the density of shorted species $\rho_{s}$ is calculated in following way:
\begin{equation}
	s_i = \begin{cases}
	1 &\text{if} \quad -log(g_i) < 5 \\
	0 &\text{if} \quad -log(g_i) \geq 5 \\
	\end{cases}
\end{equation}
\begin{equation}
	\rho_s = \sum_i^N \frac{s_i}{N}
\end{equation}
Another estimate of the conductance are the averages:
\begin{equation}
	G_1 = log \left( \sum_i^N \frac{g_i}{N} \right)
\end{equation}

\begin{equation}
	G_2 =  \sum_i^N \frac{log(g_i)}{N}
\end{equation}

\bibliographystyle{ieeetr}
\bibliography{fp}
